\documentclass{tccv}
\makeatletter
\DeclareOldFontCommand{\rm}{\normalfont\rmfamily}{\mathrm}
\DeclareOldFontCommand{\sf}{\normalfont\sffamily}{\mathsf}
\DeclareOldFontCommand{\tt}{\normalfont\ttfamily}{\mathtt}
\DeclareOldFontCommand{\bf}{\normalfont\bfseries}{\mathbf}
\DeclareOldFontCommand{\it}{\normalfont\itshape}{\mathit}
\DeclareOldFontCommand{\sl}{\normalfont\slshape}{\@nomath\sl}
\DeclareOldFontCommand{\sc}{\normalfont\scshape}{\@nomath\sc}
\makeatother
\usepackage[english]{babel}

\begin{document}


\part{Randy Heiland}

%---------------------------------------
\section{Work experience}

\begin{eventlist}

\item{2003 -- Present}
{Indiana University}
{Bloomington IN}

Associate Director/Manager/Senior System Analyst/Researcher.
Scientific software for bioinformatics, biology,
neuroscience, fluid dynamics, cybersecurity, and engineering.
Adjunct faculty in Mathematics Dept. 

\item{2005 -- 2010}
     {President}
     {Acquired Science LLC}

Consulting and scientific software development.

\item{1997 -- 2003}
     {Senior Research Scientist}
     {National Center for Supercomputing Applications (NCSA), University of
Illinois, Urbana IL}

Scientific visualization software developer, including virtual reality (CAVE) and haptics.
Taught college course in OpenGL.

\item{1993 -- 1997}
     {Computer Scientist}
     {Pacific Northwest National Lab, Richland WA}

Scientific visualization software developer for computational chemistry and image analysis.

\item{July 1992 -- Dec 1992}
     {Graduate Research Associate}
     {Los Alamos National Lab, Los Alamos NM}

Software developer for data visualization and analysis on HPC.

\item{1985 -- 1987}
     {Computer Programmer}
     {Center for Industrial Research, Oslo Norway}

Software developer for computer-aided geometric design.

\end{eventlist}

%---------------------------------------
\section{Education}

\begin{edulist}

\item{1992}
     {M.A., Mathematics}
     {(dynamical systems)}
     {Arizona State University, Tempe}

\item{1985}
     {M.S., Computer Science}
     {(computer graphics, CAGD)}
     {University of Utah, Salt Lake City}

\item{1979}
     {B.S., Computational Math}
     {Eastern Illinois University, Charleston}
     {}

\end{edulist}

%---------------------------------------
\personal
    {812-552-6127}
    {randy.heiland@gmail.com}
    {rheiland.github.io}
    {www.linkedin.com/in/rheiland}
    {researchgate.net/profile/Randy\_Heiland}
    {scholar.google.com/citations?hl=en\&user=0SeiPdoAAAAJ}
    {github.com/rheiland?tab=repositories}


%---------------------------------------
\section{Sample of Projects}

\begin{projlist}
	\item{}
	{PhysiCell (\href{http://physicell.mathcancer.org}{physicell.mathcancer.org})}
	{An open source physics-based cell simulator}
\item{}
     {CTSC (\href{http://trustedci.org}{trustedci.org})}
     {The NSF Cybersecurity Center of Excellence}
\item{}
     {SGCI (\href{http://sciencegateways.org}{sciencegateways.org})}
     {Science Gateways Community Institute}
\item{}
     {SWIP (\href{https://cacr.iu.edu/projects/swip/index.php}{cacr.iu.edu/projects/swip})}
     {Scientific Workflow Integrity with Pegasus}
\item{}
     {CompuCell3D (\href{http://compucell3d.org}{compucell3d.org})}
     {Simulation for multi-cell modeling}
\item{}
     {LifeScienceWeb}
     {Web services for bioinformatics}
\item{}
     {VisBench/VisPort}
     {Remote data visualization and analysis}
\item{}
     {ECCE (\href{http://ecce.emsl.pnl.gov/}{ecce.emsl.pnl.gov})}
     {Extensible Computational Chemistry Environment}
\end{projlist}

%---------------------------------------
\section{Software skills}

\begin{factlist}
\item{Good level}
     {C/C++, Python(+numerous pkgs), OpenGL, VTK, CMake, ParaView, MATLAB, git, 
\LaTeX, Eclipse, gdb, Linux, OSX}
 
\item{Intermediate}
     {Fortran, Java, R, CUDA, OpenCL, OpenMP, ITK, HTML, Xcode}

\item{Basic level}
     {MySQL, MPI, Boost, Django, Mathematica, Javascript, Blender, Windows}
\end{factlist}

%---------------------------------------
\section{Publications/Presentations}

\begin{projlist}
\item{}
     {\href{https://scholar.google.com/citations?hl=en&user=0SeiPdoAAAAJ&view_op=list_works&sortby=pubdate}{Google Scholar}}

\end{projlist}

%---------------------------------------
\section{References}

\begin{projlist}
%\item{yo dog}
     {Available upon request.}
\end{projlist}

\end{document}
